Quality Definitions of Qualities

### 2019-12-03 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
updated validatability

\begin{defn}
	Validatability of a software is the degree of ease in validating (checking)
	that software meets user needs. \wss{Need a citation}
\end{defn}

\begin{defn}
	Validatability means ``solving the right equations''
	\citep[p.~23]{Roache1998}.
	\oo{question about this definition}
\end{defn}

\begin{defn} \label{DefnValidatability}
	The degree of ease of evaluating software products or system to determine
	whether it satisfies specified business
	requirements.
	\url{http://softwaretestingfundamentals.com/verification-vs-validation/}
	\oo{Here I tweaked the meaning of validation to suit validatability} \oo{Only
		a few resource on validatability}
\end{defn}

Definition~\ref{DefnValidatability}.

@@

Validatability is improved by a rational process via clear documentation of the
theory and assumptions, along with an explicit statement of the systematic steps
required for experimental validation.

>>>>

\begin{defn}
	Validatability of a software is the degree of ease in validating (checking)
	that software meets user needs. \wss{Need a citation} \oo{To be removed, I don't have any citation, definition was modified from the definition of verifiability}
\end{defn}

\begin{defn}
	Validatability means solving the right equations
	\citep[p.~23]{Roache1998}.
	\oo{Validation?}
\end{defn}

\begin{defn} \label{Validatability_Selected}
   Validation is the process of evaluating software during or at the end of the development
   process to determine whether it satisfies specified business requirements \citep{softwaretestingfundamentals}.

\begin{defn}
	Validation refers to a different set
	of tasks that ensure that the software that has been built is traceable to customer requirements.
\end{defn}
\noindent \textbf{Proposed Definition}

\begin{defn}
	Requirements validation examines the specification to ensure that all
	software requirements have been stated unambiguously; that inconsistencies, omissions, and errors have been detected and corrected; and that the work products conform to the standards established for the process, the project, and the product \citep{pressman2005software}.
\end{defn}

\begin{defn}
    Software validation checks that the software product satisfies or fits the intended use (high-level checking), i.e., the software meets the user requirements, not as specification artifacts or as needs of those who will operate the software only; but, as the needs of all the stakeholders (such as users, operators, administrators, managers, investors, etc.) \citep{WikipediaVnV}
\end{defn}
\noindent \textbf{Proposed Definition}: Definition~\ref{} \oo{need to discuss this quality, we might just define validatability from validation definitions above? Resources are limited for 'validatability'}.

@@

Validatability is improved by a rational process via clear documentation of the
theory and assumptions, along with an explicit statement of the systematic steps
required for experimental validation. It is entirely possible that a product passes when verified but fails when validated. This can happen when, say, a product is built as per the specifications but the specifications themselves fail to address the user’s needs
